% Use only LaTeX2e, calling the article.cls class and 12-point type.

\documentclass[12pt]{article}

% Users of the {thebibliography} environment or BibTeX should use the
% scicite.sty package, downloadable from *Science* at
% http://www.sciencemag.org/authors/preparing-manuscripts-using-latex 
% This package should properly format in-text
% reference calls and reference-list numbers.

\usepackage{scicite}

\usepackage{times}

% The preamble here sets up a lot of new/revised commands and
% environments.  It's annoying, but please do *not* try to strip these
% out into a separate .sty file (which could lead to the loss of some
% information when we convert the file to other formats).  Instead, keep
% them in the preamble of your main LaTeX source file.


% The following parameters seem to provide a reasonable page setup.

\topmargin 0.0cm
\oddsidemargin 0.2cm
\textwidth 16cm 
\textheight 21cm
\footskip 1.0cm


%The next command sets up an environment for the abstract to your paper.

\newenvironment{sciabstract}{%
\begin{quote} \bf  }
{\end{quote}}


\date{}

\title{Orion \sourcei's disk is salty}
\begin{document}
\input{authors}
\baselineskip24pt

% Make the title.

\maketitle 

\begin{sciabstract}
    abstract
\end{sciabstract}

% This file is a draft document for a Science/Nature-style submission.  If we
% submit to one of these journals and are turned down, this can be a summary we
% pass off to NRAO for a press release.

% BAM: I removed the hard line wraps because they make my eyes twitch to look at
% while working on this.  Feel free to put them back in =).
% AG: You don't do all of your work in VIM?  Huh, weird.


Disks around high-mass stars have been difficult to identify and observe, in
part because most molecular emission lines do not uniquely trace the disk.
Observing disks around more massive stars is the critical test of whether star
formation theories developed on low-mass stars apply at higher masses.  Here,
we show that two molecular species, NaCl and KCl, appear to uniquely trace the
outer edges of the disk around the massive (15 \msun) protostellar system Orion
Source I. These molecules have previously only been detected in the atmospheres
of dying stars, and are not found in molecularly rich hot-core regions, so they
are rare enough to be unique tracers of the disk alone.  Indeed, the chemical
and physical environments in which we have detected these species are so
favorable, that we observe an unprecedented level of vibrational excitation in
their populations.    Given their apparently unique properties, we suggest that
these salts provide the best hope for unambiguous measurements of disk
properties in the high-mass regime.

Disks are ubiquitous around forming stars.  They provide the main mechanism for
mediating accretion, and, via outflows, shedding angular momentum from the system.
However, it remains uncertain whether they play an important role in high-mass
star formation, since the only definitive disk detections are around stars that
have already acquired most of their mass \citep{Girart2017a,Ginsburg2018b}.
The lack of clear disk detections is, at least in part, because there were no
known spectral lines that trace a disk and not the molecule-rich ``hot core''
in the surrounding region \citep{Goddi2018a,Cesaroni2017a}.  The central disks
may also be obscured by dust opacity at wavelengths less than 3 mm.

++++++++
BAM: Is there a distinction to be made here between the low-mass sources, where
PPDs are routinely detected through spectral lines, and which are no longer
embedded (don't have a hot-core), and these high-mass sources?  Do the
high-mass sources just not shed their 'hot core' shells at some point so we can
see the underlying 'hidden' disk like what happens in low-mass sources?  I am
not a star-formation person, so forgive me if it's a stupid question.
AG: There are high-mass stars with low-mass disks and little/no core, like
HH80/81.  
++++++++

While dozens of species have been detected in the disks around low-mass stars
\citep{McGuire2018c}, these molecules are comprised solely of a small selection
of elements: H, C, N, O, and S.  All of the molecules seen in disks are also
prevalent in the ISM, particularly in the hot cores surrounding high-mass stars
\citep{some sgr b2 reference}. In high-mass environments, this therefore
limits their utility as unique disk tracers in high-mass regions, hiding
the kinematic signatures of rotation.

At the other extreme of the stellar life cycle, in the atmospheres of dying
stars, a wealth of exotic molecules -- those containing rare elements not
commonly seen in star-forming regions -- are observed.  Stars along the
asymptotic giant branch (AGB) lose substantial mass in slow winds
\citep{Herwig2005a} that form molecules with high atomic weight elements that
rapidly condense onto dust particles.  The most notable example is that of
IRC+10216, the expanding gas cloud around the AGB star CW Leonis.  Here, NaCl,
KCl, AlCl, AlF, NaCN, and a number of other metal-bearing molecules have been
detected \citep{Agundez2012a,Zack2011a}.  In this instance, we use `metal' in
the chemist's sense of the word.  NaCl and KCl have been detected around other
AGB and post-AGB stars
\citep{Milam2007a,Highberger2003a,Sanchez-Contreras2018a}, but to our
knowledge, no detections outside of these environments have previously been
reported.

+++++ BAM: Science has a *very* strict policy about not claiming primacy (first
detections / first discovery / etc.) of anything.  I believe the above sentence
will pass OK, but the editor may object in the end.
AG: fair enough, I don't think "FIRST" is super important.  "FIRST USEFUL"
is....
+++++

Here, we report the detection of NaCl, KCl, and their $^{37}Cl$ and $^{41}$K
isotopologues in the disk around Orion Source I.  This disk was previously used
to measure the central mass of Source I as 15 \msun, although those
measurements were performed before the spectral lines belonging to NaCl and KCl
were identified \citep{Ginsburg2018b}.  Source I is the brightest object in the
Orion nebula at millimeter wavelengths and is deeply embedded within a hot core
\citep{}. Because of the high optical depth of the foreground dust, it is not
directly detected in the
mid-infrared \citep[e.g.,][]{Robberto2005a}. It is a system consisting of a
$\sim10^4$ \lsun central object with a photospheric temperature $\approx4000$ K
\citep{Testi2010a} surrounded by a $\sim0.1$ \msun disk, which we observe
nearly edge-on \citep{Plambeck2016a}.  The central source mass has been
debated, with estimates ranging from 7-20 \msun \citep{Matthews2010a,other},
but the highest-resolution data imply a central source mass $M\approx15$ \msun
from fitting a Keplerian orbital model to \water and line (now identified as
NaCl) emission profiles \citep{Ginsburg2018b}.

We performed observations with ALMA in three spectral bands at the highest
available spatial resolution, 0.03 to 0.10 arcseconds from 0.85 to 3 mm. The
spectral resolution ranged from 1.5-6.5 \kms over the same range.  We noted a
distinctive morphology in the position-velocity diagrams of several lines,
showing a clear linear gradient in velocity parallel to the disk. To obtain
higher signal-to-noise in our extracted spectra, we shifted the spectra by
their measured centroid velocities and averaged them together, obtaining a
disk-averaged spectrum.  We use this spectrum to measure and  identify lines
(see Methods).

While the most prominent spectral features are the SiO and \water lines that
have previously been observed \citep{Goddi2013a,Hirota2014a}, there were dozens
of lines that remained unidentified in our initial study \citep{Ginsburg2018b}.
We have now identified these lines as transitions of NaCl and KCl, noting the
excellent correspondence between the observed and measured/catalogued
frequencies \citep{Caris2002a,Caris2004a,Muller2005a,Lovas2005a,Pickett1998a}.
We additionally searched databases of transitions of these same species with
more quanta of vibrational excitation, and found additional matches
\citep{Barton2014a,Cabezas2016a}.

Although the detection of salts lines in a protostellar disk was surprising,
the detection of highly vibrationally excited transitions of these species is
even more so.  The detected transitions have upper-state energy levels up to
$\sim3000$ K, implying the presence of extremely hot gas or a strong radiation
field. The emission from these lines comes from a narrow range in both position
and velocity.  By fitting thin Keplerian disk models to the position-velocity
diagrams of the lines, we constrain the emission region to be 30-60 AU from
the central source.  The observed emission peaks at $\pm13$ AU above and below
the midplane of the continuum disk, which may be either a physical height or an
effect of obscuration by the optically thick continuum.  The emission does not
extend beyond this height, indicating that, unlike SiO and \water, the salts do
not trace the outflow.

Once in the gas-phase, however, we expect salts to rapidly deplete back into
dust grains \citep{Cherncheff2012a}.  Since we observe them in emission, they
must be released into the gas phase by either grain destruction, or produced
chemically from simple gas-phase precursors, likely elemental atomic gas
(either neutral or ionized Na and K).  Because previous studies have ruled out
the presence of any recombination lines in this source, and therefore
demonstrated that there is no ionized gas around Source I
\citep{Plambeck2016a,Baez-Rubio2018a}, we reject the atomic formation route.
The salts must be produced by dust destruction, most likely via sputtering by
high-energy particles \citep{Schilke1997a}.  The small scale height of the
observed salt emission therefore implies that grain destruction is an efficient
and rapid process in disk-launched winds.

The vibrationally excited transitions observed suggest that radiative
excitation is important in this environment.  The molecular transitions we
observe have high Einstein A values, in the range $\sim10^{-3}-10^0$, and
correspondingly high critical densities $n_{cr} \sim10^{8}$ \percc for v=0
and $n_{cr} \sim 10^{12}$ for $v>=1$, where $v$
is the vibrational quantum number.  Collisional excitation alone cannot explain
the different vibrational states being observed at a similar brightness level.
The rovibrational $\Delta v=1$ transitions of NaCl and KCl occur in the 25-35
\um and 35-45 \um range, respectively.  Since a blackbody with $T\sim100$ K
peaks at $\lambda\sim30$ \um, and the observed disk brightness temperature is
around 100-300 K at the radii where salts are observed, it is plausible that
strong radiation from the disk in the mid-infrared is responsible for exciting
the molecules.  However, we have not been able to assemble a self-consistent
model explaining both the rotational and vibrational excitation ladders of NaCl
or KCl.  In the supplemental material, we describe  and evaluate several other
possible excitation mechanisms that are less likely but not ruled out.

The detection of NaCl and KCl in our current dataset was serendipitous.  As a
result, the observations were not optimized for unraveling the physical and
chemical conditions underlying their presence and excitation, hindering our
ability to obtain a full picture of the exact utility of these salts as
tracers.  Nevertheless, we obtain several important conclusions from these
detections.  First and foremost, these molecular lines uniquely trace the disk
around a massive protostar, suggesting they may be an unambiguous and universal
tracer of high-mass protostellar disks. Second, since these molecules contain
atoms rarely seen in the molecular ISM because they are trapped in dust, they
may serve as a tool for directly measuring absolute metallicity in an
environment that is typically far too chemically complex and obscured for other
methods to work.
\end{document}
